---
title: "DATA 605: Homework 1"
author: "Dirk Hartog"
date: "2024-01-28"
output: html_document
---

```{r}
library(gifski)
```

## Build the first letters for both your first and last name using point plots in R

```{r initials}

x <- c(rep(-2,500),seq(-2,-1, length.out = 1000),rep(-1,250),seq(-1,-2, length.out = 1000),
       rep(0,500),seq(0,1,length.out=1000), rep(1,500))

y <- c(seq(-1,1,length.out=500), seq(1,0.5,length.out=1000), seq(0.5,-0.5,length.out=250),seq(-0.5,-1,length.out=1000),
       seq(-1,1,length.out=500),rep(0,1000), seq(-1,1,length.out=500))

z <- rbind(x,y)

plot(y~x, xlim=c(-3,3), ylim=c(-3,3), col = "turquoise",
     main = "My Initials")
```

## Write R code that will left multiply (%*%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix. 

## Use a loop that changes the transformation matrix incrementally to demonstrate 
1. shear
2. scaling
3. rotation
4. projection in animated fashion. 


### Shear

```{r shear, warning = FALSE}
x11()

for (val in seq(-3,3,length.out=50)) {
  shear_matrix <- matrix(c(2, 0, val, 1), nrow=2, ncol=2)
  shear_m <- apply(z, 2, function(x) x %*% shear_matrix)
  plot(shear_m[2,] ~ shear_m[1,], xlim=c(-8, 8), ylim=c(-8, 8), col = "turquoise", 
       main = "Shear")
  Sys.sleep(0.05)
}
```

### Scale

```{r scale, warning = FALSE}
x11()

for (val in seq(-3,3,length.out=50)) {
  scale_matrix <- matrix(c(val, 0, 0, val), nrow=2, ncol=2)
  scale_m <- apply(z, 2, function(x) x %*% scale_matrix)
  plot(scale_m[2,] ~ scale_m[1,], xlim=c(-8,8), ylim=c(-8,8), col = "turquoise", 
       main = "Scale")
  Sys.sleep(0.05)
  }
```

### Rotation

```{r rotate, warning = FALSE}
x11()

for (val in seq(-3,3,length.out=50)) {
  rotate_z <- rbind(z, numeric(3000))
  rotate_matrix <- matrix(c(cos(val), sin(val), 0, -sin(val), cos(val), 0, 0, 0, 1), nrow=3, ncol=3)
  rotate_m <- apply(rotate_z, 2, function(x) x %*% rotate_matrix)
  plot(rotate_m[2,] ~ rotate_m[1,], xlim=c(-8,8), ylim=c(-8,8), col = "turquoise",
       main = "Rotate")
  Sys.sleep(0.05)
  }
```

### Projection 

```{r projection, warning = FALSE}
x11()

for (val in seq(-3,3,length.out=50)) {
  projection_z <- rbind(z, numeric(3000))
  projection_matrix <- matrix(c(val,0,0,0,1,0,0,0,1), nrow=3, ncol=3)
  projection_m <- apply(projection_z, 2, function(x) x %*% projection_matrix)
  plot(projection_m[2,] ~ projection_m[1,], xlim=c(-8,8), ylim=c(-8,8), col = "turquoise", main = "Projection")
  Sys.sleep(0.05)
}
```

